PANCHANGE_data_preprocessing

### 2020-09-07 PANCHANGE_data_preprocessing2020-07-15.Rmd

```{r nbr cohort recode ethnicity}
if(NBR == TRUE) {
#Recode details ethnicity info
nbr.cohort.raw.id$Ethnicity_full <- recode_factor(nbr.cohort.raw.id$Ethnicity.unc,
                                             "A" = "White - British",
                                             "B" = "White - Irish",
                                             "C" = "White - Other",
                                             "D" = "Mixed - White & Black Caribbean",
                                             "E" = "Mixed - White & Black African",
                                             "F" = "Mixed - White & Asian",
                                             "G" = "Mixed - Other",
                                             "H" = "Asian - Indian",
                                             "J" = "Asian - Pakistani",
                                             "K" = "Asian - Bangladeshi",
                                             "L" = "Asian - Other",
                                             "M" = "Black - Caribbean",
                                             "N" = "Black - African",
                                             "P" = "Black - Other",
                                             "R" = "Chinese - Chinese",
                                             "S" = "Chinese - Other",
                                             "W" = NULL, ## Asking NBR what this level means
                                             "Z" = NULL,
                                             "99" = NULL)

#Match GLAD/EDGI/RAMP categories
nbr.cohort.raw.id$Ethnicity_unc <- recode_factor(nbr.cohort.raw.id$Ethnicity.unc,
                                             "A" = "White, white European or Caucasian",
                                             "B" = "White, white European or Caucasian",
                                             "C" = "White, white European or Caucasian",
                                             "D" = "Mixed or multiple ethnic origins",
                                             "E" = "Mixed or multiple ethnic origins",
                                             "F" = "Mixed or multiple ethnic origins",
                                             "G" = "Mixed or multiple ethnic origins",
                                             "H" = "Asian or Asian British (including Chinese)",
                                             "J" = "Asian or Asian British (including Chinese)",
                                             "K" = "Asian or Asian British (including Chinese)",
                                             "L" = "Asian or Asian British (including Chinese)",
                                             "M" = "Black or Black British",
                                             "N" = "Black or Black British",
                                             "P" = "Black or Black British",
                                             "R" = "Asian or Asian British (including Chinese)",
                                             "S" = "Asian or Asian British (including Chinese)",
                                             "W" = NULL, ## Asking NBR what this level means
                                             "Z" = NULL,
                                             "99" = NULL)
}
```

@@

dem.raw.id <- dem.raw.id %>%
  mutate(
    Ethnicity = 
      recode_factor(Ethnicity_unc,
        "White, white European or Caucasian" = "European",
        "Mixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
        "Asian or Asian British (including Chinese)" = "Asian or Asian British",
        "Black or Black British" = "African or African British",
        "Arab" = "Arab",
        "Other ethnic group (please specify)" = "Other ethnic group"
      )
  ) %>%
  mutate(
    Ethnicity_numeric = 
      recode(Ethnicity_unc,
        "European" = 1,
        "Mixed or multiple ethnic origins" = 2,
        "Asian or Asian British" = 3,
        "African or African British" = 4,
        "Arab" = 5,
        "Other ethnic group" = 6
      )
  )
}
```

@@

glad.employment.raw.id <- glad.employment.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(
    ID = as.numeric(ID)
    ) %>%
  select(
         Sample, # Sample
         ID, # ID
         employment.phd, # level of education - univeristy
         employment.masters_degree_or_equivalent, # level of education - univeristy
         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
         employment.bachelors_degree_or_equivalent, # level of education - univeristy
         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
         employment.o_levelsgcses_or_equivalent, # level of education - gcse
         employment.cses_or_equivalent, # level of education - cse
         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
         employment.government_work_key_workers # key worker status
         ) %>%
  add_numeric(., exclude = exclude_cols_employment) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

edgi.employment.raw.id <- edgi.employment.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
#  separate("Login ID", into = c("COPING_Sample", "COPING_ID"), sep = 6) %>% # Split ID in Sample and Number
  mutate(
    ID = as.numeric(ID),
#    COPING_ID = as.numeric(COPING_ID)
    ) %>%
  select(
         Sample, # Sample
         ID, # ID
         COPING_ID = "Login ID",
         employment.phd, # level of education - univeristy
         employment.masters_degree_or_equivalent, # level of education - univeristy
         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
         employment.bachelors_degree_or_equivalent, # level of education - univeristy
         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
         employment.o_levelsgcses_or_equivalent, # level of education - gcse
         employment.cses_or_equivalent, # level of education - cse
         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
         employment.government_work_key_workers # key worker status
         ) %>%
  add_numeric(., exclude = exclude_cols_employment_edgi) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

nbr.employment.raw.id <- nbr.employment.raw %>%
  drop_na(subjectid) %>% # Drop NAs
  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
  separate(ID.intm, into = "ID", sep = 7) %>%
  mutate(
    ID = as.numeric(ID)) %>%
  select(
         Sample, # Sample
         ID, # ID
         employment.phd, # level of education - univeristy
         employment.masters_degree_or_equivalent, # level of education - univeristy
         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
         employment.bachelors_degree_or_equivalent, # level of education - univeristy
         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
         employment.o_levelsgcses_or_equivalent, # level of education - gcse
         employment.cses_or_equivalent, # level of education - cse
         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
         employment.government_work_key_workers # key worker status
         ) %>%
  add_numeric(., exclude = exclude_cols_employment) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

ramp.employment.raw.id <- ramp.employment.raw %>%
  drop_na(`Login ID`) %>% # Drop NAs
  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(
    ID = as.numeric(ID)
    ) %>%
  select(
         Sample, # Sample
         ID, # ID
         employment.what_is_your_highest_level_of_education, #highest level of edcuation
         employment.government_work_key_workers # key worker status
         ) %>%
  add_numeric(., exclude = exclude_cols_employment) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

## Key worker status
```{r Key worker}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
#create numeric version of the variable
employment.raw.id <- employment.raw.id %>%
  mutate(
    key_worker_numeric =
      case_when(
        employment.government_work_key_workers_numeric == "0" ~ 0,
        employment.government_work_key_workers_numeric > 0 ~ 1
      )
    )

@@

employment.raw.id %>%
  freq(key_worker)
}
```

@@

  edgi.mhd2.raw.id <- edgi.mhd2.raw %>%
    drop_na(externalDataReference) %>% # Drop NAs
    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
    mutate(ID = as.numeric(ID)) %>%
    select(
      Sample, # Sample
      ID, # ID
    mhd.depression = demographics.depression,
    mhd.pregnancy_depression = demographics.pregnancy_depression,
    mhd.premenstrual_dysphoric_disorder_pmdd = demographics.premenstrual_dysphoric_disorder_pmdd,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder = demographics.anxiety_nerves_or_generalised_anxiety_disorder,
    mhd.social_anxiety_or_social_phobia = demographics.social_anxiety_or_social_phobia,
    mhd.specific_phobia_e.g._phobia_of_flying = demographics.specific_phobia_e.g._fear_of_flying, # fear instead of phobia
    mhd.agoraphobia = demographics.agoraphobia,
    mhd.panic_disorder = demographics.panic_disorder,
    mhd.panic_attacks = demographics.panic_attacks,
    mhd.obsessivecompulsive_disorder_ocd = demographics.obsessivecompulsive_disorder_ocd,
    mhd.obsessive_compulsive_related_disorders = demographics.obsessive_compulsive_related_disorders,
    mhd.body_dysmorphic_disorder_bdd = demographics.body_dysmorphic_disorder,
    mhd.mania_hypomania_bipolar_or_manicdepression = demographics.mania_hypomania_bipolar_or_manicdepression,
    mhd.schizophrenia = demographics.schizophrenia,
    mhd.type_psychosis_psychotic_illness = demographics.psychosis_type_psychotic_illness, # word type psychosis changed order compared to GLAD 
    mhd.personality_disorder_diagnosed = demographics.diagnosed_personality_disorder, # named differently in EDGI
    mhd.posttraumatic_stress_disorder_ptsd = demographics.posttraumatic_stress_disorder_ptsd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder = demographics.autism_spectrum_disorder_asd, # different name in EDGI
    mhd.body_dysmorphic_disorder_bdd = demographics.body_dysmorphic_disorder,
    mhd.personality_disorder = demographics.personality_disorder, # routing variable in EDGI is named differently; renamed here to match GLAD
    mhd.attention_deficit_hyperactivity_disorder = demographics.attention_deficit_hyperactivity_disorder,
    mhd.none_of_the_above = demographics.none_of_the_above.1,
    mhd.dont_know = demographics.dont_know,
    mhd.prefer_not_to_answer = demographics.prefer_not_to_answer.3,
    mhd.none_of_the_above.1 = demographics.none_of_the_above.8,
    mhd.dont_know.1 = demographics.dont_know.7,
    mhd.prefer_not_to_answer.1 = demographics.prefer_not_to_answer.11,
    mhd.other_please_tell_us_more = demographics.other.1
    ) %>%
    add_column(
      mhd.schizoaffective_disorder = NA_character_
    ) %>%
    add_numeric(., exclude = exclude_cols_mhd2) %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

>>>>

```{r nbr cohort recode ethnicity}
if(NBR == TRUE) {
#Recode details ethnicity info
nbr.cohort.raw.id$Ethnicity_full <- recode_factor(nbr.cohort.raw.id$Ethnicity.unc,
                                             "A" = "White - British",
                                             "B" = "White - Irish",
                                             "C" = "White - Other",
                                             "D" = "Mixed - White & Black Caribbean",
                                             "E" = "Mixed - White & Black African",
                                             "F" = "Mixed - White & Asian",
                                             "G" = "Mixed - Other",
                                             "H" = "Asian - Indian",
                                             "J" = "Asian - Pakistani",
                                             "K" = "Asian - Bangladeshi",
                                             "L" = "Asian - Other",
                                             "M" = "Black - Caribbean",
                                             "N" = "Black - African",
                                             "P" = "Black - Other",
                                             "R" = "Chinese - Chinese",
                                             "S" = "Chinese - Other",
                                             "W" = "White - not disclosed", ## Asking NBR what this level means
                                             "Z" = NULL,
                                             "99" = NULL)

#Match GLAD/EDGI/RAMP categories
nbr.cohort.raw.id$Ethnicity_unc <- recode_factor(nbr.cohort.raw.id$Ethnicity.unc,
                                             "A" = "White, white European or Caucasian",
                                             "B" = "White, white European or Caucasian",
                                             "C" = "White, white European or Caucasian",
                                             "D" = "Mixed or multiple ethnic origins",
                                             "E" = "Mixed or multiple ethnic origins",
                                             "F" = "Mixed or multiple ethnic origins",
                                             "G" = "Mixed or multiple ethnic origins",
                                             "H" = "Asian or Asian British (including Chinese)",
                                             "J" = "Asian or Asian British (including Chinese)",
                                             "K" = "Asian or Asian British (including Chinese)",
                                             "L" = "Asian or Asian British (including Chinese)",
                                             "M" = "Black or Black British",
                                             "N" = "Black or Black British",
                                             "P" = "Black or Black British",
                                             "R" = "Asian or Asian British (including Chinese)",
                                             "S" = "Asian or Asian British (including Chinese)",
                                             "W" = "White, white European or Caucasian", 
                                             "Z" = NULL,
                                             "99" = NULL)
}
```

@@

dem.raw.id <- dem.raw.id %>%
  mutate(
    Ethnicity = 
      recode_factor(Ethnicity_unc,
        "White, white European or Caucasian" = "European",
        "Mixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
        "Asian or Asian British (including Chinese)" = "Asian or Asian British",
        "Black or Black British" = "African or African British",
        "Arab" = "Arab",
        "Other ethnic group (please specify)" = "Other ethnic group"
      )
  ) %>%
  mutate(
    Ethnicity_numeric = 
      recode(Ethnicity,
        "European" = 1,
        "Mixed or multiple ethnic origins" = 2,
        "Asian or Asian British" = 3,
        "African or African British" = 4,
        "Arab" = 5,
        "Other ethnic group" = 6
      )
  )
}
```

@@

glad.employment.raw.id <- glad.employment.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(
    ID = as.numeric(ID)
    ) %>%
  select(
         Sample, # Sample
         ID, # ID
         employment.phd, # level of education - univeristy
         employment.masters_degree_or_equivalent, # level of education - univeristy
         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
         employment.bachelors_degree_or_equivalent, # level of education - univeristy
         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
         employment.o_levelsgcses_or_equivalent, # level of education - gcse
         employment.cses_or_equivalent, # level of education - cse
         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
         employment.government_work_key_workers, # key worker status
         employment.government_work_key_workers, # key worker status
         employment.unemployed, #key worker routing variable
         employment.zerohours_contract, #key worker routing variable
         employment.stayathome_parent_or_carer, #key worker routing variable
         employment.retired, #key worker routing variable
         employment.student_gcse_or_a_level, #key worker routing variable
         employment.student_university, #key worker routing variable
         employment.became_unemployed, #key worker routing variable
         employment.furloughed_or_paid_leave_government_funded, #key worker routing variable
         employment.furloughed_or_paid_leave_company_funded, #key worker routing variable
         employment.paid_leave_furloughed #key worker routing variable
         ) %>%
  add_numeric(., exclude = exclude_cols_employment) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

edgi.employment.raw.id <- edgi.employment.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
#  separate("Login ID", into = c("COPING_Sample", "COPING_ID"), sep = 6) %>% # Split ID in Sample and Number
  mutate(
    ID = as.numeric(ID),
#    COPING_ID = as.numeric(COPING_ID)
    ) %>%
  select(
         Sample, # Sample
         ID, # ID
         COPING_ID = "Login ID",
         employment.phd, # level of education - univeristy
         employment.masters_degree_or_equivalent, # level of education - univeristy
         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
         employment.bachelors_degree_or_equivalent, # level of education - univeristy
         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
         employment.o_levelsgcses_or_equivalent, # level of education - gcse
         employment.cses_or_equivalent, # level of education - cse
         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
         employment.government_work_key_workers, # key worker status
         employment.government_work_key_workers, # key worker status
         employment.unemployed, #key worker routing variable
         employment.zerohours_contract, #key worker routing variable
         employment.stayathome_parent_or_carer, #key worker routing variable
         employment.retired, #key worker routing variable
         employment.student_gcse_or_a_level, #key worker routing variable
         employment.student_university, #key worker routing variable
         employment.became_unemployed, #key worker routing variable
         employment.furloughed_or_paid_leave_government_funded, #key worker routing variable
         employment.furloughed_or_paid_leave_company_funded, #key worker routing variable
         employment.paid_leave_furloughed #key worker routing variable
         ) %>%
  add_numeric(., exclude = exclude_cols_employment_edgi) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

nbr.employment.raw.id <- nbr.employment.raw %>%
  drop_na(subjectid) %>% # Drop NAs
  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
  separate(ID.intm, into = "ID", sep = 7) %>%
  mutate(
    ID = as.numeric(ID)) %>%
  select(
         Sample, # Sample
         ID, # ID
         employment.phd, # level of education - univeristy
         employment.masters_degree_or_equivalent, # level of education - univeristy
         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
         employment.bachelors_degree_or_equivalent, # level of education - univeristy
         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
         employment.o_levelsgcses_or_equivalent, # level of education - gcse
         employment.cses_or_equivalent, # level of education - cse
         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
         employment.government_work_key_workers, # key worker status
         employment.unemployed, #key worker routing variable
         employment.zerohours_contract, #key worker routing variable
         employment.stayathome_parent_or_carer, #key worker routing variable
         employment.retired, #key worker routing variable
         employment.student_gcse_or_a_level, #key worker routing variable
         employment.student_university, #key worker routing variable
         employment.became_unemployed, #key worker routing variable
         employment.furloughed_or_paid_leave_government_funded, #key worker routing variable
         employment.furloughed_or_paid_leave_company_funded, #key worker routing variable
         employment.paid_leave_furloughed #key worker routing variable
         ) %>%
  add_numeric(., exclude = exclude_cols_employment) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

ramp.employment.raw.id <- ramp.employment.raw %>%
  drop_na(`Login ID`) %>% # Drop NAs
  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(
    ID = as.numeric(ID)
    ) %>%
  select(
         Sample, # Sample
         ID, # ID
         employment.what_is_your_highest_level_of_education, #highest level of edcuation
         employment.government_work_key_workers, # key worker status
         employment.government_work_key_workers, # key worker status
         employment.unemployed, #key worker routing variable
         employment.zerohours_contract, #key worker routing variable
         employment.stayathome_parent_or_carer, #key worker routing variable
         employment.retired, #key worker routing variable
         employment.student_gcse_or_a_level, #key worker routing variable
         employment.student_university, #key worker routing variable
         employment.became_unemployed, #key worker routing variable
         employment.furloughed_or_paid_leave_government_funded, #key worker routing variable
         employment.furloughed_or_paid_leave_company_funded, #key worker routing variable
         employment.paid_leave_furloughed #key worker routing variable
         ) %>%
  add_numeric(., exclude = exclude_cols_employment) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

## Key worker status
```{r Key worker}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
#create numeric version of the variable
employment.raw.id <- employment.raw.id %>%
  mutate(
    key_worker_numeric =
      case_when(
        employment.government_work_key_workers_numeric == "0" ~ 0,
        employment.government_work_key_workers_numeric > 0 ~ 1,
        employment.unemployed_numeric == "1" ~ 0,
        employment.stayathome_parent_or_carer_numeric == "1" ~ 0,
        employment.retired_numeric == "1" ~ 0, 
        employment.became_unemployed_numeric == "0" ~ 0,
        employment.student_gcse_or_a_level_numeric == "1" ~ 0,
        employment.student_university_numeric == "1" ~ 0,
        employment.furloughed_or_paid_leave_government_funded_numeric == "1" ~ 0,
        employment.furloughed_or_paid_leave_company_funded_numeric == "1" ~ 0,
        employment.paid_leave_furloughed_numeric == "1" ~ 0
      )
    )

@@

employment.raw.id %>%
  freq(key_worker)
}

@@

  edgi.mhd2.raw.id <- edgi.mhd2.raw %>%
    drop_na(externalDataReference) %>% # Drop NAs
    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
    mutate(ID = as.numeric(ID)) %>%
    select(
      Sample, # Sample
      ID, # ID
    mhd.depression = demographics.depression,
    mhd.pregnancy_depression = demographics.pregnancy_depression,
    mhd.premenstrual_dysphoric_disorder_pmdd = demographics.premenstrual_dysphoric_disorder_pmdd,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder = demographics.anxiety_nerves_or_generalised_anxiety_disorder,
    mhd.social_anxiety_or_social_phobia = demographics.social_anxiety_or_social_phobia,
    mhd.specific_phobia_e.g._phobia_of_flying = demographics.specific_phobia_e.g._fear_of_flying, # fear instead of phobia
    mhd.agoraphobia = demographics.agoraphobia,
    mhd.panic_disorder = demographics.panic_disorder,
    mhd.panic_attacks = demographics.panic_attacks,
    mhd.obsessivecompulsive_disorder_ocd = demographics.obsessivecompulsive_disorder_ocd,
    mhd.obsessive_compulsive_related_disorders = demographics.obsessive_compulsive_related_disorders,
    mhd.body_dysmorphic_disorder_bdd = demographics.body_dysmorphic_disorder_bdd,
    mhd.mania_hypomania_bipolar_or_manicdepression = demographics.mania_hypomania_bipolar_or_manicdepression,
    mhd.schizophrenia = demographics.schizophrenia,
    mhd.type_psychosis_psychotic_illness = demographics.psychosis_type_psychotic_illness, # word type psychosis changed order compared to GLAD 
    mhd.personality_disorder_diagnosed = demographics.diagnosed_personality_disorder, # named differently in EDGI
    mhd.posttraumatic_stress_disorder_ptsd = demographics.posttraumatic_stress_disorder_ptsd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder = demographics.autism_spectrum_disorder_asd, # different name in EDGI
    mhd.personality_disorder = demographics.personality_disorder, # routing variable in EDGI is named differently; renamed here to match GLAD
    mhd.attention_deficit_hyperactivity_disorder = demographics.attention_deficit_hyperactivity_disorder,
    mhd.none_of_the_above = demographics.none_of_the_above.1,
    mhd.dont_know = demographics.dont_know,
    mhd.prefer_not_to_answer = demographics.prefer_not_to_answer.3,
    mhd.none_of_the_above.1 = demographics.none_of_the_above.8,
    mhd.dont_know.1 = demographics.dont_know.7,
    mhd.prefer_not_to_answer.1 = demographics.prefer_not_to_answer.11,
    mhd.other_please_tell_us_more = demographics.other.1
    ) %>%
    add_column(
      mhd.schizoaffective_disorder = NA_character_
    ) %>%
    add_numeric(., exclude = exclude_cols_mhd2) %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
